RJObject Paper

### 2014-06-23 Documents/Paper/ms.tex
Notation
Number to change uses heavy tailed dist

A proposal
for an object involves transforming its parameters to $[0, 1]$ using $F$,
making the proposal in terms of $u$, and then transforming back.
Specifically, the proposal chooses
a new value $x_i'$ from the current value $x_i$ as follows:
\begin{eqnarray}
u_i &=& F(x_i; \alpha)\\
u_i' &=& \textnormal{mod}\left(u_i + \delta_u, 1\right)\\
x_i' &=& F^{-1}(u_i'; \alpha).
\end{eqnarray}

>>>>

A proposal
for an object involves transforming its parameters to $[0, 1]$ using $F$,
making the proposal in terms of $u$, and then transforming back.
Specifically, the proposal chooses
a new value $x_i'$ from the current value $x_i$ as follows:
\begin{eqnarray}
u_i &=& F(x_i; \alpha)\\
u_i' &=& \textnormal{mod}\left(u_i + \delta_u, 1\right)\\
x_i' &=& G(u_i'; \alpha).
\end{eqnarray}
where $\delta_u$ is drawn from a heavy-tailed distribution.

Choosing just one object to change is most appropriate when the DNS
distribution is very constrained. When it is close to the prior, bolder
proposals that change more than one object at a time are possible. Hence,
we choose the number of objects to change from a heavy tailed distribution
wherer the most probable value is 1 but there is also a nontrivial probability
of proposing to change $\sim N$ objects at once.
